Title

### 2012-09-05 inc/plasmon/plasmon.tex
improving the introduction to SPP

\subsection{Driving the Plasmon}

Every material has an intrinsic plasma frequency given by 
\begin{equation}
  \omega_{P} = \sqrt{\frac{n e^2}{\varepsilon_{0} m^*}}
\end{equation}
where $n$ is the electron density and $m*$ is the effective mass of the material.
In order to drive a plasmon on the surface of a material, the portion of the laser wave-vector parallel to the plasmon ($k_{Lx}$) must be matched to the wave-vector of the surface plasmon.
\begin{equation}
  k_{P} = k_{Lx} + i k_{G}
\end{equation}

>>>>

\subsection{Driving the Surface Plasmon}

As the name suggests, a plasmon is the quasiparticle of plasma oscillation.
Electrons in a material can couple with electromagnetic fields, in this case a laser field, and oscillate accordingly.
When this occurs at the surface of a material, the resultant quasiparticles are called ``surface plasmon-polaritons.''
Since these will be the only plasmons discussed in this paper, the word ``plasmon'' will be used interchangeably for the name ``surface plasmon-polaritons.''
%TODO should this be formalized, either one way (SPP) or the other

The mathematical formalism of surface plasmon-polaritons is a lengthy subject and well described elsewhere \cite{cottam_introduction_2004,concepts_2002}.

Every material has an intrinsic plasma frequency given by 
\begin{equation}
  \omega_{P} = \sqrt{\frac{\rho_{e} e^2}{\varepsilon_{0} m^*}}
\end{equation}
where $\rho_{e}$ is the electron density and $m*$ is the effective mass of the material.
And in the most simple (undamped) approximations, the dielectric function of the material may be written in terms of this constant.
\begin{equation} \label{eq:dielectric_as_omega}
  \varepsilon(\omega) = 1 - \frac{ \omega_{P}^2 }{ \omega^2 }
\end{equation}

At the interface of a vacuum and such a simple material material, contstraints on the material parameters which may allow surface plasmons result in the condition that the dielectric constant at the oscillation frequency of the surface plasmon $ \varepsilon(\omega_{SP}) = -1 $.
Substituting this result into \ref{eq:dielectric_as_omega} show that this frequency of oscillation is simply related to intrinsic plasma frequency by
\begin{equation}
  \omega_{SP} = \omega_{P} / \sqrt{2}
\end{equation}

Further, plasmons carry momentum whose magnitude is given by
\begin{equation}
  k_{P}^2 = \frac{\omega^2}{c^2} \left( \frac{\varepsilon_{1} \varepsilon_{2}}{\varepsilon_{1} + \varepsilon_{2}} \right)
\end{equation}
but of course for a vacuum interface this is simplified to 
\begin{equation}
  k_{SP}^2 = \frac{\omega^2}{c^2} \left( \frac{ \varepsilon }{ 1 + \varepsilon } \right)
\end{equation}

In order to drive a plasmon on the surface of a material, the portion of the laser wave-vector parallel to the plasmon ($k_{Lx}$) must be matched to the wave-vector of the surface plasmon.
\begin{equation}
  k_{SP} = k_{Lx} + \imath k_{G}
\end{equation}
